$K$-corrections and filter transformations \\ in the ultraviolet, optical, and near infrared

### 2006-10-04 docs/paper/kcorrect-aj-v3/ms.tex
add
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@566 75dff457-8751-0410-ab1a-cd701654ce6b

\documentclass[12pt,preprint]{aastex}
\usepackage{amsmath}
\usepackage{epsfig}

@@

There are limitations to all stellar population synthesis libraries,
and our results are therefore restricted to be at best as good as our
input models. There are some well-known areas of uncertainty in the
stellar populations models in the UV and IR. In the UV, old
populations sometimes contain extreme horizontal branch stars that
have lost their envelopes and are thus extremely hot, that dominate
the flux at $\lambda \sim 1500$ \AA. There is certainly no physical
model that predicts when this happens, and no consensus about how
these stars should be accounted for in isochrone synthesis (that is,
what fraction of stars undergo this phase as a function of mass and
metallicity). While the models of \cite{bruzual03a} do contain
post-AGB and planetary nebula phases that provide FUV flux in old
populations, they do not contain extreme horizontal branch stars or
other candidates that might provide more of the ``UV-excess'' seen in
elliptical galaxies (\citealt{greggio90a, brown00a}).  In the near-IR,
the spectra of thermally-pulsating asymptotic giant branch (TP-AGB)
stars may dominate the flux in certain intermediate age populations
(2--3 Gyr). With respect to these phases, \citet{bruzual03a} use
models that are calibrated to observations of TP-AGB stars
nearby. \citet{maraston05a} show that a different choice of TB-AGB
models can produce significantly higher flux in the NIR at
intermediate ages. Thus, the choices for AGB and post-AGB evolution we
make here by using the models \cite{bruzual03a} are not definitive,
but we do not address these controversies here and they remain an
uncertainty in the physical interpretation of galaxy fluxes.  We do
note that for low redshift galaxies our results from BC03 do explain
most galaxies' colors (though see below for our discussion of the high
redshift GOODS sample).

@@

\begin{thebibliography}{43}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

>>>>

\documentclass[12pt,preprint]{aastex}

@@

There are limitations to all stellar population synthesis libraries,
and our results are therefore restricted to be at best as good as our
input models. There are some well-known areas of uncertainty in the
stellar populations models in the UV and IR. In the UV, old
populations sometimes contain extreme horizontal branch stars that
have lost their envelopes and are thus extremely hot, that dominate
the flux at $\lambda \sim 1500$ \AA. There is certainly no physical
model that predicts when this happens, and no consensus about how
these stars should be accounted for in isochrone synthesis (that is,
what fraction of stars undergo this phase as a function of mass and
metallicity). While the models of \cite{bruzual03a} do contain
post-AGB and planetary nebula phases that provide FUV flux in old
populations, they do not contain extreme horizontal branch stars or
other candidates that might provide more of the ``UV-excess'' seen in
elliptical galaxies (\citealt{greggio90a, brown00a}).

In the near-IR, the spectra of thermally-pulsating asymptotic giant
branch (TP-AGB) stars may dominate the flux in certain intermediate
age populations (0.5--2 Gyr).  \citet{maraston05a} show that including
TP-AGB spectra based on nearby TP-AGB stars, rather than on the models
of \citet{vassiliadis93a} used by \citet{bruzual03a}, produces
significantly higher flux in the NIR at intermediate ages. Thus, the
choices for AGB and post-AGB evolution we make here by using the
models \cite{bruzual03a} are not definitive, but we do not address
these controversies here and they remain an uncertainty in the
physical interpretation of galaxy fluxes.  We do note that for low
redshift galaxies our results from BC03 do explain most galaxies'
colors (though see below for our discussion of the high redshift GOODS
sample).

@@

\begin{thebibliography}{44}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Vassiliadis} \& {Wood}(1993)}]{vassiliadis93a}
{Vassiliadis}, E. \& {Wood}, P.~R. 1993, \apj, 413, 641
